Super-resolution of Aeromagnetic Survey Data

### 2023-10-12 paper2.tex
Consolidate bibliography at end of doc
Update vector figures

\begin{figure}[hbtp]
    \includegraphics[width=\linewidth]{fig/p2/temp_lte.png}
    \caption[The LTE architecture]{
        A simplified representation of the super-resolution LTE network.
        The encoder is marked as \(E_\phi{}\).
        \(f_\Theta{}\) is an MLP network used as the decoder for image reconstruction.
        A long-range skip connection with simple upscaling is marked with an arrow.
        The LTE network block performs high-resolution upscaling of extracted features in the Frequency domain.
        Simplified from \textcite{leeLocalTextureEstimator2022}.
    }
    \label{fig:ltenet}
\end{figure}

>>>>

\begin{figure}[hbtp]
    \includegraphics[width=\linewidth]{fig/p2/ltenet.pdf}
    \caption[The LTE architecture]{
        The LTE super-resolution network is structured as an autoencoder.
        The encoder can take the form of RDN (prior the upsampling and reconstruction, see \Cref{fig:rdn}), or transformer-based networks.
        The decoder is an MLP network, and is used for image reconstruction.
        A long-range skip connection with simple upscaling allows low-resolution features common to both LR and SR to bypass the network.
        The LTE network block performs high-resolution upscaling of extracted features in the Frequency domain.
        Simplified from \textcite{leeLocalTextureEstimator2022}, where the LTE block is further detailed.
    }
    \label{fig:ltenet}
\end{figure}
